Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY

### 2015-12-06 Manuscript/Manuscript.Rnw
changes

  listing <- function(x, options){
    paste("\\begin{lstlisting}[style=Rsettings]\n",
      x, "\\end{lstlisting}\n", sep = "")}
  knit_hooks$set(source=listing, output=listing)
@
<<setup, include=FALSE,cache=FALSE>>=
# Libraries
## Install Most Current Version
library(devtools)#;dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("harrelfe/Hmisc");dev_mode(on=F)
## Attach Remaining
library(corrplot)
library(ggplot2);library(ggExtra)
library(Hmisc)
library(MplusAutomation)
library(NlsyLinks)
library(plyr);library(psych)
library(stargazer)
library(tables)
library(xtable)
#
# File Structure
file_drive= "C:"
##file_drive="E:"
directory = paste0(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI")
#
# Functions
## source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")
## cor_1star
### Prints out clean correlation matrix. If you want to replace the upper triangle with the sample size, toggle include.n, whose default is FALSE.
cor_1star <- function(x,digit=3,sig=.05,include.n=FALSE){ 
  require(Hmisc) 
  x <- as.matrix(x) 
  R <- rcorr(x)$r 
  p <- rcorr(x)$P

  ## define notions for significance levels; spacing is important.
  mystars <- ifelse(p < sig, "* ", " ")

  ## truncate the matrix that holds the correlations to two decimal
  R <- format(round(cbind(rep(-1.11, ncol(x)), R), digit))[,-1]

  ## build a new matrix that includes the correlations with their appropriate stars 
  Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x)) 
  diag(Rnew) <- paste(diag(R), " ", sep="") 
  rownames(Rnew) <- colnames(x) 
  colnames(Rnew) <- paste(colnames(x), "", sep="")

  Rnew <- as.matrix(Rnew)
  if(!include.n){
    ## remove upper triangle
    Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
    Rnew <- as.data.frame(Rnew) 
    Rnew <- cbind(Rnew[1:length(Rnew)-1])
  }
  if(include.n){
    #replace upper triangle with sample size
    require(psych)
    ct<-corr.test(x)
    ct<-as.matrix(ct$n)
    Rnew[upper.tri(Rnew, diag = TRUE)] <- ct[upper.tri(ct, diag = TRUE)]
    Rnew <- as.data.frame(Rnew) 
    Rnew <- cbind(Rnew[1:length(Rnew)])#-1])
  }

  return(Rnew) 
}
##
## ROUNDING FUNCTIONS
### Function rounds to three digits and defaults to na.rm = TRUE
### Cor
Cor <- function(x,digit=3, use="pairwise.complete.obs") {
  round(cor(x, use = use),digit)}

@@

capture.output(xtable(cor_1star(matrix_afi_diff,digit=2,sig=.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_diffafireliable_z.tex"))
               capture.output(xtable(cor_1star(matrix_tt_z,digit=2,sig=.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_ttafireliable_z.tex"))
capture.output(xtable(cor_1star(matrix_g1,digit=2,sig=.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_sibintreliable_z.tex"))

@@

### Link
dsOutcomes$SubjectTag<-dsOutcomes$MCASEID*100
dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")
dsSinglez <- CreatePairLinksSingleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c(
"AFI_G2","AFI_G2z","SEX_G2")
)
dsDz <- CreatePairLinksDoubleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c(
"AFI_G2","AFI_G2z","SEX_G2")
)
### Export Matrix
matrix_afi_cousincor<-data.frame(dsSinglez$AFI_G2z_S1,dsSinglez$AFI_G2z_S2)
capture.output(xtable(cor_1star(matrix_afi_cousincor,2,.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_sibafig2_z.tex"))
Cor(matrix_afi_cousincor)

## Gen2 Mean Intelligence
### Test-Retest
#### Import
G_G2_9.5 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_910811.csv",sep=""), header=FALSE)
names(G_G2_9.5)<-c("CASEID","ASEID","G_G2_9.5","G_SE_G2_9.5","MCASEID")
G_G2_10.5 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_1011912.csv",sep=""), header=FALSE)
names(G_G2_10.5)<-c("CASEID","ASEID","G_G2_10.5","G_SE_G2_10.5","MCASEID")
G_G2_11.5 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_11121013.csv",sep=""), header=FALSE)
names(G_G2_11.5)<-c("CASEID","ASEID","G_G2_11.5","G_SE_G2_11.5","MCASEID")
#### Merge
temp<-merge(G_G2_9.5[c(1,3)],G_G2_10.5[c(1,3)],by="CASEID",all=T)
G_G2<-merge(temp,G_G2_11.5[c(1,3)],by="CASEID",all=T)
#### Export Matrix Test Retest
capture.output(xtable(cor_1star(G_G2[2:4],2,.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_ttintreliable_z.tex"))

@@

%%%%%%%%%%%% Introduction %%%%%%%%%%%%
%\section{Introduction}
\section{ }\vspace{-.8cm}
% Introduce the Major Problem
\input{../Common/content/introduction/introduce_the_problem.txt}\\
\input{../Common/content/introduction/importance_of_problem.txt}

% Relevant Scholarship
%\subsection{Relevant Scholarship}
\input{../Common/content/introduction/relevant_scholarship.txt}\\

% Current Study
\subsection{Current Study}
\input{../Common/content/introduction/current_study.txt}

%%%%%%%%%%%% Method %%%%%%%%%%%%
\section{Method}
% Research Design
\subsection{Research Design}
\input{../Common/content/method/design.txt}
%
% Sample
\subsection{Sample}
\input{../Common/content/method/subjects.txt}
%
% Tetrads
\subsection{Tetrads}
\input{../Common/content/method/tetrad.txt}
%
% Age at First Intercourse
\subsection{Age at First Intercourse}
\input{../Common/content/method/AFI.txt}
%
%%%%%%%%%%%% Measurement %%%%%%%%%%%%
\section{Measures}
%
% Gen1
\subsection{Generation 1}
\input{../Common/content/method/Gen1measures.txt}
%
% Gen2
\subsection{Generation 2}
\input{../Common/content/method/Gen2measures.txt}
%
% Difference Score Reliability
\subsection{Reliability of Difference Scores}
\input{../Common/content/method/diffscores.txt}
<<calculationint,cache=TRUE>>=
sigmax = sqrt(1.1881)
sigmay = sigmax
rxx = .87
ryy = rxx
rxy=.67

(sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) /
  (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
@
<<calculationint2,include=FALSE,cache=TRUE>>=
r.diff.intelligence <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) /
  (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
@
The calculated reliability of Generation 1's differences in AFQT was \Sexpr{r.diff.intelligence}, acceptable, but lower than the empirical correlation we derived for cousin differences.\\

We can also calculate the difference score reliability for Generation 2 AFI, by substituting the following values into equation \ref{equation_Lord1963},
where, \begin{itemize}
\item $\sigma_{x}^{2}$ and $\sigma_{y}^{2}$ are 4.41 (from Table \vref{table_summary_stats_sibinsampleg2}) %the variance of Gen2 Mean AFI, 
\item $\rho_{xx'}$ and $\rho_{yy'}$ are .76 (from Table \vref{table_measurement_trt_g1afi}), 
\item $\rho_{xy}$ is the AFI correlation between first born cousins is .099.(from Figure \vref{plot_between})\end{itemize}
<<calculationafi,cache=TRUE>>=
sigmax = sqrt(4.41)
sigmay = sigmax
rxx = .76
ryy = rxx
rxy=.099
(sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) / 
  (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
@
<<calculationafi2,cache=TRUE,include=FALSE>>=
r.diff.afi<- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) / 
  (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
@
 Gen2 Mean AFI difference scores were also reliable (r = \Sexpr{r.diff.afi}) and comparable to Generation 1 sibling differences.
%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
\input{../Common/content/results/results.txt}
%
% Between Family
\subsection{Between Family}
\input{../Common/content/results/results_between.txt}
%
% Within Family
\subsection{Within Family}
\input{../Common/content/results/results_within.txt}
%
%%%%%%%%%%%% Discussion %%%%%%%%%%%%
\section{Discussion}
\input{../Common/content/discussion/discussion.txt}

%%%%%%%%%%%% Tables %%%%%%%%%%%%
\newpage\section{Tables}
% Descriptive Statistics
\subsection{Descriptive Statistics}
%% Sibling in Sample Summary Stats
%%% Gen 1
\begin{longtable}{@{\extracolsep{5pt}}lcccccc}
\caption{Gen1 Summary Statistics by Sibling Status.}\label{table_summary_stats_sibinsampleg1}
\partialinput{2}{10}{../Common/content/tables/table_summary_stats_sibinsampleg1.tex}
\end{longtable}\linebreak
%%% Gen 2
\begin{longtable}{@{\extracolsep{5pt}}lcccccc}
\caption{Gen2 Summary Statistics by Sibling Status.}\label{table_summary_stats_sibinsampleg2}
\partialinput{2}{10}{../Common/content/tables/table_summary_stats_sibinsampleg2.tex}
%% AFI by Gender, Race, and Gender by Race
\npnoround
\begin{longtable}{@{\extracolsep{5pt}}lllcc}
\caption{Gen2 Mean AFI by Gender, Race, and Gender by Race.}\label{table_afi_race_gender}
\partialinput{2}{18}{../Common/content/tables/table_summary_stats_AFIRACEGENDER.tex}
% Measurement
\subsection{Measurement}
%% Age 9
%%% Measurement Model
\begin{longtable}{@{\extracolsep{5pt}}cc} 
\caption{Gen2 Measurement Model.}\label{table_gen2measurement_9}
 & g at Age 9.5 \\ 
\partialinput{12}{34}{../Common/content/tables/table_g2_9measurement.tex}
%%% Factor Loadings
\begin{longtable}{@{\extracolsep{5pt}}cccccc} 
\caption{Gen2 Factor Loadings.}\label{table_g2loading_9}
 & Test & Estimate & S.E. & Est./.S.E. & P.Value \\  
\partialinput{12}{17}{../Common/content/tables/table_g2loading_9.tex}
% Difference Scores
\subsection{Difference Scores}
%% AFI
%%% AFI Test-Retest Gen 1
\begin{minipage}{\linewidth}
\begin{longtable}{@{\extracolsep{5pt}}rlll} \caption{Correlation of Gen1 Self-Reported AFI Across 1983-1985 }\label{table_measurement_trt_g1afi}
\partialinput{6}{12}{../Common/content/tables/table_ttafireliable_z.tex}
\linebreak
%%% AFI Sibling Differences
\begin{longtable}{@{\extracolsep{5pt}}rlll} \caption{Correlation of Gen1 Sibling Differences in Self-Reported AFI across 1983-1985 (Standardized by Gender)}\label{table_measurement_diffafireliable_z.tex}
\partialinput{6}{12}{../Common/content/tables/table_diffafireliable_z.tex}
%% Intelligence
%%% Test-retest Gen 2 intelligence
\begin{longtable}{@{\extracolsep{5pt}}rlll} \caption{Correlation of Gen2 Aggregated Intelligence across Ages 9.5, 10.5, 11.5 }\label{table_measurement_trt_g2int}
\partialinput{6}{12}{../Common/content/tables/table_ttintreliable_z.tex}
\end{longtable}\end{minipage}
\pagebreak
\newpage
%%% Cousin Difference Scores Gen 2 intelligence
%%%% First Born Child
\begin{minipage}{\linewidth}
\begin{longtable}{@{\extracolsep{5pt}}rlll} \caption{Correlation of Gen2 First Born Cousin Differences in Intelligence across Ages 9.5-11.5}\label{table_measurement_diffintreliable_z}
\partialinput{6}{12}{../Common/content/tables/table_diffintreliable_z.tex}
%%%%
%%%% First Born Daughter
\begin{longtable}{@{\extracolsep{5pt}}rlll} \caption{Correlation of Gen2 First Female Cousin Differences in Intelligence across Ages 9.5-11.5}\label{table_measurement_diffintreliable_g}
\partialinput{6}{12}{../Common/content/tables/table_diffintreliable_g.tex}
%%%%
%%%% First Born Son
\begin{longtable}{@{\extracolsep{5pt}}rlll} \caption{Correlation of Gen2 First Male Cousin Differences in Intelligence across Ages 9.5-11.5}\label{table_measurement_diffintreliable_b}
\partialinput{6}{12}{../Common/content/tables/table_diffintreliable_b.tex}
\end{longtable}\end{minipage}
\pagebreak
% Between Family Analyses
\begin{landscape}
%% Mom -> Child
\caption{Gen1 Mean Intelligence $\rightarrow$ Gen2 Mean AFI}\label{table_Mean_Mom_Intelligence_Mean_Child_AFI_9}
\partialinput{10}{22}{../Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_9.tex}
%% Child -> Child
\caption{Gen2 Mean Intelligence $\rightarrow$ Gen2 Mean AFI}\label{table_Mean_Child_Intelligence_Mean_Child_AFI_9}
\partialinput{10}{22}{../Common/content/tables/table_Mean_Child_Intelligence_Mean_Child_AFI_9.tex}
%% Mom Child -> Child
\caption{Mean Joint Intelligence $\rightarrow$ Gen2 Mean AFI}\label{table_Mean_Joint_Intelligence_Mean_Child_AFI_9}
\partialinput{10}{23}{../Common/content/tables/table_Mean_Joint_Intelligence_Mean_Child_AFI_9.tex}
% Within Family Analyses
%% Mom -> Child
\caption{Gen1 Dif Intelligence $\rightarrow$ Gen2 Dif AFI}\label{table_Dif_Mom_Intelligence_Dif_Child_AFI_9}
\partialinput{10}{24}{../Common/content/tables/table_Dif_Mom_Intelligence_Dif_Child_AFI_9.tex}
%% Child -> Child
\caption{Gen2 Dif Intelligence $\rightarrow$ Gen2 Dif AFI}\label{table_Dif_Child_Intelligence_Dif_Child_AFI_9}
\partialinput{10}{24}{../Common/content/tables/table_Dif_Child_Intelligence_Dif_Child_AFI_9.tex}
%% Mom Child -> Child
\caption{Dif Joint Intelligence $\rightarrow$ Gen2 Dif AFI}\label{table_Dif_Joint_Intelligence_Dif_Child_AFI_9}
\partialinput{10}{26}{../Common/content/tables/table_Dif_Joint_Intelligence_Dif_Child_AFI_9.tex}
\end{longtable}\end{landscape}

%%%%%%%%%%%% Figures %%%%%%%%%%%%
\section{Figures}
\begin{center}
\captionof{figure}{Smoothed Density Plots of AFI by Sex and Race}
\label{plot_afi_by_race_sex}
<<plot_afi_by_race_sex,fig=TRUE,echo=FALSE,cache=FALSE,echo=FALSE, fig.height=5*.6, fig.width=5,out.width=".8\\paperwidth",warning=FALSE>>=
# Color Blind Palette 
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#000000")
# Data Prep
dataframe<-data.frame(Gen2AFIConcor_2,Gen2AFIConcor$Intel_G2)
names(dataframe)<- c("CASEID","MCASEID","RACE","SEX","AFI","Intel")

@@

ggplot(dataframe, aes(x=AFI, colour=RACE, group=RACEbySEX, linetype = SEX))+ geom_density(fill=NA,adjust=2)+ theme_bw() + theme(axis.text=element_text(size=10), axis.title=element_text(size=12), plot.title=element_text(size=12)) +  theme(legend.position="right",  legend.justification=c(1, 0.5)) +   xlab("AFI") + ylab("Density") +scale_colour_manual(values= c("#56B4E9", "#009E73", "#CC79A7")) + coord_cartesian(ylim=c(0,0.30), xlim=c(12,25))
@
\end{center}
\pagebreak
%
\begin{center}
<<plot_corplotmatrix_within,fig=TRUE,echo=FALSE,cache=FALSE,fig.height=7*.6, fig.width=7,out.width="1.1\\paperwidth",warning=FALSE>>=
# Croat Cor Matrix Plot for Between Family and Sibling Effects
dataframe<- LinkedMDAN_discord_AFI_z_9
C<-dataframe[,c(8,13,23,24,26,31,41,42)]#,56,57,66,67,70,71
##
## Rename variables
names(C)<-c("Intel_Mom_1","AFI_Mom_1","AFI_Kid_1","Intel_Kid_1","Intel_Mom_2","AFI_Mom_2","AFI_Kid_2","Intel_Kid_2")
##
## Reorder Variables
C<-C[c("Intel_Mom_1","Intel_Mom_2","Intel_Kid_1","Intel_Kid_2","AFI_Mom_1","AFI_Mom_2","AFI_Kid_1","AFI_Kid_2")]
##
## Plot
corrplot(Cor(C), method = "ellipse",type="lower",tl.col="black")
@
\captionof{figure}{Within Family Correlations}
\label{plot_within}
\end{center}
\pagebreak
%
\begin{center}
<<plot_corplotmatrix_between,fig=TRUE,echo=FALSE,cache=FALSE, fig.height=7*.6, fig.width=7,out.width="1.1\\paperwidth",warning=FALSE>>=
# Create Cor Matrix Plot for Between Family and Sibling Effects
dataframe<- LinkedMDAN_discord_AFI_z_9
C<-dataframe[,c(56,57,66,67,70,71,89,90)]
##
## Rename variables
names(C)<-c("AFI_Mom_diff","AFI_Mom_mean","Intel_Mom_diff","Intel_Mom_mean","AFI_Kid_diff","AFI_Kid_mean","Intel_Kid_mean","Intel_Kid_diff")
##
## Reorder Variables
C<-C[c("Intel_Mom_mean","Intel_Mom_diff","Intel_Kid_mean","Intel_Kid_diff","AFI_Mom_mean","AFI_Mom_diff","AFI_Kid_mean","AFI_Kid_diff")]
##
## Plot
corrplot(Cor(C), method = "ellipse",type="lower",tl.col="black")
@
\captionof{figure}{Between Family Correlations}
\label{plot_between}
\end{center}
\pagebreak

\begin{center}
<<plot_spaghetti,fig=TRUE,echo=FALSE,cache=FALSE, fig.height=7, fig.width=7,out.width=".8\\paperwidth",warning=FALSE>>=
# Plot Set up
mytheme <- theme_classic() %+replace% 
  theme(axis.title.x = element_text(face="bold",angle=0), 
        axis.title.y = element_text(face="bold",angle=90)) 
# Data Set Up
dataframe<- LinkedMDAN_discord_AFI_z_9
C<-dataframe[,c(2,8,13,23,24,26,31,41,42)]#,56,57,66,67,70,71
##
## Rename variables
names(C)<-c("ID","Intel_Mom_1","AFI_Mom_1","AFI_Kid_1","Intel_Kid_1","Intel_Mom_2","AFI_Mom_2","AFI_Kid_2","Intel_Kid_2")
##
## Reorder Variables
C<-C[c("ID","Intel_Mom_1","Intel_Mom_2","Intel_Kid_1","Intel_Kid_2","AFI_Mom_1","AFI_Mom_2","AFI_Kid_1","AFI_Kid_2")]

C2<-C
names(C2)<-c("ID","Intel_Mom_2","Intel_Mom_1","Intel_Kid_2","Intel_Kid_1","AFI_Mom_2","AFI_Mom_1","AFI_Kid_2","AFI_Kid_1")
C2<-C2[c("ID","Intel_Mom_1","Intel_Mom_2","Intel_Kid_1","Intel_Kid_2","AFI_Mom_1","AFI_Mom_2","AFI_Kid_1","AFI_Kid_2")]

Stack<-rbind(C,C2)

Stack$slope <- (Stack$AFI_Kid_2-Stack$AFI_Kid_1)/(Stack$Intel_Kid_2-Stack$Intel_Kid_1)
Stack$slopebinary<- as.numeric(NA)
Stack$slopebinary[Stack$slope>0]<- 1
Stack$slopebinary[Stack$slope<0]<- -1
Stack$slopebinary[Stack$slope==0]<- 0
Stack$slopebinary<-factor(Stack$slopebinary, levels=c("1", "0", "-1"), labels=c("Positive", "Zero", "Negative"))
Stack2<-Stack[,c(1,2,4,6,8,11)]

Stack3<-Stack2
### Generate within vs. between slopes

x <- rep(-5:5, length=233)

btwn <- Cor(data.frame(Stack2$AFI_Kid_1,Stack2$Intel_Kid_1))[1,2] * x

within <- Mean(Stack$slope)* x
within2 <- Median(Stack$slope)* x
df <- data.frame(x, y=btwn)

# create a copy of original data, but set y = x
# this data will be used for the one-to-one line
df2 <- data.frame(x, y=within)
df22 <- data.frame(x, y=within2)
# bind original and 'one-to-one data' together
df3 <- rbind.data.frame(df, df2, df22)

# create a grouping variable to separate stat_smoothers based on original and one-to-one data 
df3$grp <- as.factor(rep(1:3, each = nrow(df)))

df3$grp<-factor(df3$grp, levels=c("1", "2", "3"), labels=c("Between Family Slope", "Within Family Slope (mean)", "Within Family Slope (median)"))
df3=df3[1:698,]
# If you rather want to stack the two keys in the legend you can add:
# guide = guide_legend(direction = "vertical")
#...as argument in scale_colour_manual
p1 <- ggplot(data = Stack2, aes(x = Intel_Kid_1, y = AFI_Kid_1, group = ID, color=slopebinary )) +
  mytheme + scale_colour_manual(name = "Within Family \nSlope",values= c("#56B4E9", "#009E73", "#CC79A7")) +
  labs(list(title = "Gen2. Within Family Spaghetti Plot of \nAFI by Intelligence", y = "Gender Standardized AFI", x = "Standardized Intelligence")) + 
  geom_line(size=1,alpha=0.4)  + theme(legend.position="right",  legend.justification=c(1, 0.5)) + coord_cartesian(xlim = c(Min(Stack2$Intel_Kid_1),Max(Stack2$Intel_Kid_1) ),ylim = c(Min(Stack2$AFI_Kid_1),Max(Stack2$AFI_Kid_1)))  +
  stat_smooth(aes(x = df3$x, y = df3$y, group = df3$grp, linetype=df3$grp), method = "lm", se = FALSE, size = 1) + scale_linetype_manual(name = "Slopes",values=c("solid","twodash", "dotted"))

p1 #+
 # geom_smooth(method = "lm", se = FALSE, size = 1)
\captionof{figure}{Spaghetti Plot. The mean Within-Family Slope is \Sexpr{Mean(Stack$slope)}; the median Within-Family Slope is \Sexpr{Median(Stack$slope)}}
\label{plot_spaghetti}
\end{center}
%%%%%%%%%%%% References %%%%%%%%%%%%
\bibliography{Projects-AFI}
%%%%%%%%%%%% Appendix %%%%%%%%%%%%

>>>>

  listing <- function(x, options){
    paste("\\begin{lstlisting}[style=Rsettings]\n",
      x, "\\end{lstlisting}\n", sep = "")}
  knit_hooks$set(source=listing, output=listing)
@
<<setup, include=FALSE>>=
# Libraries
## Install Most Current Version
library(devtools)#;dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("harrelfe/Hmisc");dev_mode(on=F)
## Attach Remaining
library(corrplot)
library(ggplot2);library(ggExtra)
library(Hmisc)
library(MplusAutomation)
library(NlsyLinks)
library(plyr);library(psych)
library(stargazer)
library(tables)
library(xtable)
#
# File Structure
file_drive= "C:"
##file_drive="E:"
directory = paste0(file_drive,"/Dropbox/Work/Research/Projects/Legacy/NLSY/AFI")
#
# Functions
## source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")
## cor_1star
### Prints out clean correlation matrix. If you want to replace the upper triangle with the sample size, toggle include.n, whose default is FALSE.
cor_1star <- function(x,digit=3,sig=.05,include.n=FALSE){ 
  require(Hmisc) 
  x <- as.matrix(x) 
  R <- rcorr(x)$r 
  p <- rcorr(x)$P 
   ## truncate the matrix that holds the correlations to two decimal
  R <- format(round(cbind(rep(-1.11, ncol(x)), R), digit))[,-1] 
  ## build a new matrix that includes the correlations with their appropriate stars 
  Rnew <- R

  if(is.numeric(sig)){
  ## define notions for significance levels; spacing is important.
  mystars <- ifelse(p < sig, "* ", " ")
  ## build a new matrix that includes the correlations with their appropriate stars 
  Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x)) }
  diag(Rnew) <- paste(diag(R), " ", sep="") 
  rownames(Rnew) <- colnames(x) 
  colnames(Rnew) <- paste(colnames(x), "", sep="")

  Rnew <- as.matrix(Rnew)
  if(!include.n){
    ## remove upper triangle
    Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
    Rnew <- as.data.frame(Rnew) 
    Rnew <- cbind(Rnew[1:length(Rnew)-1])
  }
  if(include.n){
    #replace upper triangle with sample size
    require(psych)
    ct<-corr.test(x)
    ct<-as.matrix(ct$n)
    Rnew[upper.tri(Rnew, diag = TRUE)] <- ct[upper.tri(ct, diag = TRUE)]
    Rnew <- as.data.frame(Rnew) 
    Rnew <- cbind(Rnew[1:length(Rnew)])#-1])
  }
  return(Rnew) 
}
##
## ROUNDING FUNCTIONS
### Function rounds to three digits and defaults to na.rm = TRUE
### Cor
Cor <- function(x,digit=3, use="pairwise.complete.obs") {
  round(cor(x, use = use),digit)}

@@

capture.output(xtable(cor_1star(matrix_afi_diff,digit=2,sig=NA,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_diffafireliable_z.tex"))
               capture.output(xtable(cor_1star(matrix_tt_z,digit=2,sig=NA,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_ttafireliable_z.tex"))

capture.output(xtable(cor_1star(matrix_g1,digit=2,sig=NA,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_sibintreliable_z.tex"))

@@

### Link
dsOutcomes$SubjectTag<-dsOutcomes$MCASEID*100
dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")
dsSinglez <- CreatePairLinksSingleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c(
"AFI_G2","AFI_G2z","SEX_G2")
)
dsDz <- CreatePairLinksDoubleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c(
"AFI_G2","AFI_G2z","SEX_G2")
)
### Export Matrix
matrix_afi_cousincor<-data.frame(dsSinglez$AFI_G2z_S1,dsSinglez$AFI_G2z_S2)
capture.output(xtable(cor_1star(matrix_afi_cousincor,2,NA,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_sibafig2_z.tex"))
Cor(matrix_afi_cousincor)

## Gen2 Mean Intelligence
### Test-Retest
#### Import
G_G2_9.5 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_910811.csv",sep=""), header=FALSE)
names(G_G2_9.5)<-c("CASEID","ASEID","G_G2_9.5","G_SE_G2_9.5","MCASEID")
G_G2_10.5 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_1011912.csv",sep=""), header=FALSE)
names(G_G2_10.5)<-c("CASEID","ASEID","G_G2_10.5","G_SE_G2_10.5","MCASEID")
G_G2_11.5 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_11121013.csv",sep=""), header=FALSE)
names(G_G2_11.5)<-c("CASEID","ASEID","G_G2_11.5","G_SE_G2_11.5","MCASEID")
#### Merge
temp<-merge(G_G2_9.5[c(1,3)],G_G2_10.5[c(1,3)],by="CASEID",all=T)
G_G2<-merge(temp,G_G2_11.5[c(1,3)],by="CASEID",all=T)
#### Export Matrix Test Retest
A<-G_G2[2:4]
names(A)<-c("Age 9.5","Age 10.5","Age 11.5")
capture.output(xtable(cor_1star(A,2,.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_ttintreliable_z.tex"))

@@

%%%%%%%%%%%% Introduction %%%%%%%%%%%%
%\section{Introduction}
\section{ }\vspace{-.8cm}
% Introduce the Major Problem
\input{../Common/content/writing/introduction.txt}
% Current Study
\subsection{Current Study, Summary}
\input{../Common/content/writing/current_study.txt}

%%%%%%%%%%%% Method %%%%%%%%%%%%
\section{Method}
\subsection{Research Design}
\input{../Common/content/writing/design.txt}
%
% Sample
\subsection{Sample}
\input{../Common/content/writing/subjects.txt}
%
% Tetrads
\subsection{Tetrads}
\input{../Common/content/writing/tetrad.txt}
%
%%%%%%%%%%%% Measurement %%%%%%%%%%%%
% Age at First Intercourse
\subsection{Measures}
\input{../Common/content/writing/AFI.txt}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Smoothed Density Plots of AFI by Sex and Race}
\label{plot_afi_by_race_sex}
\begin{center}
<<plot_afi_by_race_sex,fig=TRUE,echo=FALSE,cache=TRUE,echo=FALSE, fig.height=5*.6, fig.width=5,out.width=".8\\paperwidth",warning=FALSE>>=
  # Color Blind Palette 
  cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#000000")
  # Data Prep
  dataframe<-data.frame(Gen2AFIConcor_2,Gen2AFIConcor$Intel_G2)
  names(dataframe)<- c("CASEID","MCASEID","RACE","SEX","AFI","Intel")

@@

  ggplot(dataframe, aes(x=AFI, colour=RACE, group=RACEbySEX, linetype = SEX))+ geom_density(fill=NA,adjust=2)+ theme_bw() + theme(axis.text=element_text(size=10), axis.title=element_text(size=12), plot.title=element_text(size=12)) +  theme(legend.position="right",  legend.justification=c(1, 0.5)) +   xlab("AFI") + ylab("Density") +scale_colour_manual(values= c("#56B4E9", "#009E73", "#CC79A7")) + coord_cartesian(ylim=c(0,0.30), xlim=c(12,25))
  @
\end{center}
\end{minipage}
%
% Intelligence
\input{../Common/content/writing/intelligence.txt}
%
% Difference Score Reliability
\subsection{Reliability of Difference Scores}
<<calculationalphadif,cache=TRUE,include=FALSE>>=
# Intelligence
sigmax = sqrt(1.1881)
sigmay = sigmax
rxx = .87
ryy = rxx
rxy=.67
r.diff.intelligence <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) /(sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
#AFI
sigmax = sqrt(4.41)
sigmay = sigmax
rxx = .76
ryy = rxx
rxy=.099
r.diff.afi <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) / (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
@
Our design assumes that the difference scores of our measures are reliable. We've reported the test-retest reliability of Gen2 intelligence and Gen1 AFI in earlier sections. Here, we report the test-retest reliability of the pairwise differences of those measures. 
\subsubsection{AFI} Comparing sibling differences in AFI as reported in 1983 and 1984 (n = 783 pairs) we found a strong correlation (r = .76). The sample of sibling pairs with complete information in 1985 was too small (n = 12 pairs) to compare to the other two years. Regardless, sibling differences in self-reported AFI appear reliable. Because we could not estimate test-retest reliabilities for Generation 2, we calculated the reliability using Lord's equation (\citeyear{Lord1963}). Generation 2 Mean AFI difference scores were also reliable (r = \Sexpr{r.diff.afi}) and comparable to Generation 1 sibling differences.

\subsubsection{Intelligence} Cousin differences in intelligence as assessed at ages 9.5, 10.5, and 11.5 were correlated using three different linking methods (Mixed, Daughers, Sons). Reliabilities across linking methods was consistent and high (min r = .86; max r = .95). However, we could not estimate test-retest reliabilities for Generation 1; we calculated the reliability using Lord's equation (\citeyear{Lord1963}). The calculated reliability of Generation 1's differences in AFQT was \Sexpr{r.diff.intelligence}, acceptable, but lower than the empirical correlation we derived for cousin differences.

%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
\input{../Common/content/results/results.txt}
%
% Between Family
\subsection{Between-Family Analyses}
\input{../Common/content/results/results_between.txt}
%
% Within Family
\subsection{Within-Family Analyses}
\input{../Common/content/results/results_within.txt}
%
%%%%%%%%%%%% Discussion %%%%%%%%%%%%
\section{Discussion}
\input{../Common/content/discussion/discussion.txt}

%%%%%%%%%%%% References %%%%%%%%%%%%
\bibliography{Projects-AFI}
  %%%%%%%%%%%% Appendix %%%%%%%%%%%%
   \begin{landscape} \appendix\label{appen}
  %
  % Age 10.5 Replication
  \section{Age 10.5 Replication}\label{appen10}
  %% Between Family
